Who Cares About Crackdowns? Exploring the Role of Trust in Individual Philanthropy

### 2021-04-17 manuscript/manuscript.Rmd
Full support for all rmarkdown outputs

```{r libraries-data, include=FALSE}
library(tidyverse)
library(targets)
library(kableExtra)
library(patchwork)
library(scales)
library(janitor)
library(glue)
library(here)

@@

Closing civic space not just resulted in net losses of income to INGOs, particularly through official bilateral and multilateral aid [@DupuyPrakash:2018], it has also affected how and where funds are allocated. Following the passage of anti-NGO laws, official donors move funds away from contentious causes such as human rights, media, corruption, advocacy, among others, towards tamer and more regime-compatible causes such as health, education [@ChaudhryHeiss:2018]. The latter trend has also been exacerbated by a preference among donors working in official aid and the democracy promotion establishment to gradually increase funding directed towards tame causes, at the expense of more contentious causes. This is because many tame causes can have easily quantifiable, measurable outputs, which makes it clear to show a program’s effectiveness over time (Bush 2015).

We argue that individual private donors can help fill in an important gap. Individual donors do not use the same performance-based metrics as official donors [@desaikharas]. Rather, individual donors often use heuristics to simply their decision-making, making cursory judgments about an organization’s issue area, mission, vision, and values and seek out supplementary information from friends, family, and acquaintances [@TBPrakash:2017; @SzperPrakash:2011]. Due to these differences, individual donors can help address some of the challenges arising from reduced public funding available to INGOs. To be clear, we are not arguing that giving by individual donors would be a perfect substitute for NGOs net loss of income or income for certain programs, but rather, an important supplement to reduced funding from foreign sources. Moreover, it would also be a supplement to private funding from foundations towards international nonprofits which has not been as adversely affected, with foundations continue to channel funds to countries with hostile legal environments [@NeedlesWolcheckSato:2018].

@@

```{r organization-attributes-full}
orgs$org_attributes %>% 
  select(Organization, `Issue area`, `Organizational practices`, 
         `Funding sources`, `Relationship with government`) %>% 
  kbl(align = "lllll",
      caption = "Organization attributes varied in the experiment. Each participant saw repeated combinations of attributes, with one attribute randomly selected from each column.") %>% 
  kable_styling()
```

@@

```{r sample-details}
participant_summary %>% 
  select(Question = clean_name,
         Response = level,
         N = count,
         `%` = nice_prop) %>% 
  kbl(align = "lllcc",
      caption = "Summary of individual respondent characteristics") %>% 
  pack_rows(index = table(fct_inorder(participant_summary$category))) %>%
  collapse_rows(columns = 1, valign = "top") %>% 
  kable_styling()
```

@@

```{r persona-attributes}
personas$persona_attributes %>% 
  kbl(align = "lll",
      caption = "Individual attributes varied in the simulation, resulting in 64 persona profiles") %>% 
  kable_styling()
```

```{r organization-attributes}
orgs$org_attributes %>% 
  select(`Issue area`, `Relationship with government`, `Funding`) %>% 
  kbl(align = "lll",
      caption = "Organization attributes varied in the simulation, resulting in 24 hypothetical organizations") %>% 
  kable_styling()
```

@@

example_persona_results_small %>% 
  mutate(Organization = text_spec(Organization, bold = Organization == "Total")) %>% 
  kbl(align = "lcc",
      caption = "Sample simulation output",
      escape = FALSE) %>% 
  kable_styling()
```

>>>>

```{r libraries-data, include=FALSE}
library(tidyverse)
library(targets)
library(kableExtra)
library(huxtable)
library(patchwork)
library(scales)
library(janitor)
library(glue)
library(here)

@@

Closing civic space not just resulted in net losses of income to INGOs, particularly through official bilateral and multilateral aid [@DupuyPrakash:2018], it has also affected how and where funds are allocated. Following the passage of anti-NGO laws, official donors move funds away from contentious causes such as human rights, media, corruption, advocacy, among others, towards tamer and more regime-compatible causes such as health, education [@ChaudhryHeiss:2018]. The latter trend has also been exacerbated by a preference among donors working in official aid and the democracy promotion establishment to gradually increase funding directed towards tame causes, at the expense of more contentious causes. This is because many tame causes can have easily quantifiable, measurable outputs, which makes it clear to show a program's effectiveness over time [@Bush:2015].

We argue that individual private donors can help fill in an important gap. Individual donors do not use the same performance-based metrics as official donors [@desaikharas]. Rather, individual donors often use heuristics to simply their decision-making, making cursory judgments about an organization's issue area, mission, vision, and values and seek out supplementary information from friends, family, and acquaintances [@TBPrakash:2017; @SzperPrakash:2011]. Due to these differences, individual donors can help address some of the challenges arising from reduced public funding available to INGOs. To be clear, we are not arguing that giving by individual donors would be a perfect substitute for NGOs net loss of income or income for certain programs, but rather, an important supplement to reduced funding from foreign sources. Moreover, it would also be a supplement to private funding from foundations towards international nonprofits which has not been as adversely affected, with foundations continue to channel funds to countries with hostile legal environments [@NeedlesWolcheckSato:2018].

@@

```{r organization-attributes-full}
tbl_org_attributes_caption <- "Organization attributes varied in the experiment. Each participant saw repeated combinations of attributes, with one attribute randomly selected from each column."

tbl_org_attributes <- orgs$org_attributes %>% 
  select(Organization, `Issue area`, `Organizational practices`, 
         `Funding sources`, `Relationship with government`)

if (!is_docx) {
  tbl_org_attributes %>%
    kbl(align = c("l", "l", "l", "l", "l"),
        booktabs = TRUE, linesep = "\\addlinespace",
        caption = tbl_org_attributes_caption) %>% 
    kable_styling() %>% 
    column_spec(1:5, width = "0.17\\\\textwidth")
} else {
  tbl_org_attributes %>% 
    hux() %>% 
    set_font_size(10) %>%
    set_all_padding(3) %>% 
    set_top_border(1, everywhere) %>%
    set_bottom_border(c(1, 5), everywhere) %>%
    set_width(1) %>% 
    set_wrap(TRUE) %>% 
    huxtable::set_caption(tbl_org_attributes_caption) %>% 
    huxtable::as_flextable() %>% 
    flextable::font(fontname = "Times New Roman")
}
```

@@

```{r sample-details}
tbl_participant_summary_caption <- "Summary of individual respondent characteristics"

tbl_participant_summary <- participant_summary %>% 
  select(Question = clean_name,
         Response = level,
         N = count,
         `%` = nice_prop)

if (!is_docx) {
  tbl_participant_summary %>% 
    kbl(align = c("l", "l", "c", "c"),
        longtable = TRUE, booktabs = TRUE, linesep = "",
        caption = tbl_participant_summary_caption) %>% 
    pack_rows(index = table(fct_inorder(participant_summary$category)),
              latex_gap_space = "1.5em", indent = FALSE) %>%
    collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>% 
    kable_styling(latex_options = c("repeat_header"))
} else {
  tbl_participant_summary %>% 
    hux() %>% 
    set_font_size(10) %>%
    set_all_padding(3) %>% 
    set_align(everywhere, 1:2, "left") %>% 
    set_align(everywhere, 3:4, "center") %>% 
    merge_repeated_rows(col = 1) %>% 
    insert_row("Demographics", "", "", "", after = 1) %>% 
    insert_row("\nAttitudes toward charity", "", "", "", after = 23) %>% 
    insert_row("\nPolitics, ideology, and religion", "", "", "", after = 51) %>%
    merge_cells(2, 1:2) %>%
    merge_cells(24, 1:2) %>%
    merge_cells(52, 1:2) %>%
    set_bold(1, everywhere) %>%
    set_bold(c(2, 24, 52), everywhere) %>%
    set_top_border(1, everywhere) %>%
    set_bottom_border(1, everywhere) %>%
    set_bottom_border(c(7, 9, 14, 21, 23,
                        26, 33, 40, 47, 51,
                        55, 57, 59, 66, 73, 75, 78, 80), 
                      everywhere) %>% 
    set_width(1) %>% 
    set_col_width(1, 0.25) %>%
    set_col_width(2, 0.4) %>%
    set_col_width(3:4, 0.1) %>%
    set_wrap(TRUE) %>% 
    huxtable::set_caption(tbl_participant_summary_caption) %>% 
    huxtable::as_flextable() %>% 
    flextable::font(fontname = "Times New Roman")
}
```

@@

```{r persona-attributes}
tbl_persona_attributes_caption <- "Individual attributes varied in the simulation, resulting in 64 persona profiles"

tbl_persona_attributes <- personas$persona_attributes

if (!is_docx) {
  tbl_persona_attributes %>% 
    kbl(align = c("l", "l", "l"),
        booktabs = TRUE, linesep = "\\addlinespace",
        caption = tbl_persona_attributes_caption) %>% 
    kable_styling() %>% 
    column_spec(1, width = "0.3\\\\textwidth") %>% 
    column_spec(2, width = "0.3\\\\textwidth") %>% 
    column_spec(3, width = "0.3\\\\textwidth")
} else {
  tbl_persona_attributes %>% 
    hux() %>% 
    set_font_size(10) %>%
    set_all_padding(3) %>% 
    set_align(everywhere, everywhere, "left") %>% 
    set_top_border(1, everywhere) %>%
    set_bottom_border(c(1, 9), everywhere) %>%
    set_width(1) %>% 
    set_wrap(TRUE) %>% 
    huxtable::set_caption(tbl_persona_attributes_caption) %>% 
    huxtable::as_flextable() %>% 
    flextable::font(fontname = "Times New Roman")
}
```

```{r organization-attributes}
tbl_org_attributes_caption <- "Organization attributes varied in the simulation, resulting in 24 hypothetical organizations"

tbl_org_attributes <- orgs$org_attributes %>% 
  select(`Issue area`, `Relationship with government`, `Funding`)

if (!is_docx) {
  tbl_org_attributes %>% 
    kbl(align = c("l", "l", "l"),
        booktabs = TRUE, linesep = "\\addlinespace",
        caption = tbl_org_attributes_caption) %>% 
    kable_styling()
} else {
  tbl_persona_attributes %>% 
    hux() %>% 
    set_font_size(10) %>%
    set_all_padding(3) %>% 
    set_align(everywhere, everywhere, "left") %>% 
    set_top_border(1, everywhere) %>%
    set_bottom_border(c(1, 9), everywhere) %>%
    set_width(1) %>% 
    set_wrap(TRUE) %>% 
    huxtable::set_caption(tbl_org_attributes_caption) %>% 
    huxtable::as_flextable() %>% 
    flextable::font(fontname = "Times New Roman")
}
```

@@

example_personal_results_caption <- "Sample simulation output"

if (!is_docx) {
  example_persona_results_small %>% 
    # mutate(Organization = text_spec(Organization, bold = Organization == "Total")) %>% 
    kbl(align = c("l", "c", "c"),
        booktabs = TRUE, linesep = "\\addlinespace",
        caption = example_personal_results_caption) %>% 
    kable_styling() %>% 
    column_spec(1, width = "0.2\\\\textwidth") %>% 
    column_spec(2, width = "0.35\\\\textwidth") %>% 
    column_spec(3, width = "0.35\\\\textwidth")
} else {
  example_persona_results_small %>% 
    hux() %>% 
    set_font_size(10) %>%
    set_all_padding(3) %>% 
    set_align(everywhere, 1, "left") %>% 
    set_align(everywhere, 2:3, "center") %>% 
    set_top_border(1, everywhere) %>%
    set_bottom_border(c(1, 12, 13), everywhere) %>%
    set_width(1) %>% 
    set_wrap(TRUE) %>% 
    huxtable::set_caption(example_personal_results_caption) %>% 
    huxtable::as_flextable() %>% 
    flextable::font(fontname = "Times New Roman")
}
```
